\chapter{Expert system solutions}
\label{cap:annexB}

This appendix details the solutions offered by FENCE's fuzzy recommendation system. These are divided into two groups: on the one hand, the recommendations related to proposed communication strategies (\emph{Solution 1}, \emph{Solution 2}, ..., \emph{Solution 9}), independent of the \emph{Mediator}, \emph{Training} and \emph{Supervisor} solutions, focused on reducing socio-cultural distances or favouring the efforts of less experienced users.

\section{Communication solutions}

\begin{itemize}

\item \textbf{Solution 1}: asynchronous means are recommended given a low time overlap. The communication is adapted to the age of the users and their level of English, proposing as main means of communication e-mail and conventional documentation.\newline

\item \textbf{Solution 2}: asynchronous means are recommended given the low time overlap. Given an average fluency in English, Wikis and e-mail are encouraged as the main means of communication, with the possibility of relying on conventional documentation.\newline

\item \textbf{Solution 3}: asynchronous means adapted to low time overlap are recommended. Given the high level of English of both users, email, chats and Wikis are recommended as the main means of communication, depending on the circumstances.\newline

\item \textbf{Solution 4}: synchronous means are advisable in view of the high time overlap. Given the high level of English of the users, the use of the conventional phone calls is recommended.\newline

\item \textbf{Solution 5}: synchronous media that encourage communication at low levels of English, such as chat rooms, are recommended.\newline

\item \textbf{Solution 6}: asynchronous means are recommended given the low time overlap. As there is a common command of English, corporate chats are recommended as the main means of communication (e.g. Teams or Jira).\newline

\item \textbf{Solution 7}: asynchronous means are recommended to suit the low level of English of the users. Recommended media capable of meeting these requirements are Slack and Github.\newline

\item \textbf{Solution 8}: synchronous means are recommended as the time overlap is high. Given the high level of English of the users, video calls through applications such as Zoom, Teams, Skype, Hangouts, etc. are recommended.\newline

\item \textbf{Solution 9}: synchronous media adapted to a low level of English are recommended, such as synchronous chats from tools like Zoom, Teams, Skype, WhatsApp, Telegram, etc.\newline

\end{itemize}

\section{Other solutions}

\begin{itemize}

\item \textbf{\emph{Mediator} solution}: given the high cultural differences between users, a mediator is recommended to intercede between them in order to ensure proper communication.\newline

\item \textbf{\emph{Training} solution}: socio-cultural training is recommended to reinforce communication between users: manuals, training or any other awareness solution.\newline

\item \textbf{\emph{Supervisor} solution}: given the low user's experience, the assignment of the following supervisor is proposed: ...\newline

\end{itemize}